Checkpoint 3

### 2020-04-22 Checkpoint3.Rmd
Update Checkpoint3.Rmd

plot_usmap(data = Finaldata, values = "percent_asian", color = "white") + 
  scale_fill_continuous( name = "Percent Asian", label = scales::comma) + 
  theme(legend.position = "right") + ggtitle("Percent of Residents that Identify as Asian") + 
  theme(
plot.title = element_text(color="Black", size=14, face="bold")
)

@@

ggplot(Finaldata, aes(x = per_capita_income, fill = StateColor)) + 
    geom_density(alpha = .8)+ ggtitle("Income per Capita") + xlab("$") + ylab("Density")

ggplot(Finaldata, aes(x = per_capita_income)) + 
    geom_density()+ ggtitle("Income per Capita") + xlab("$") + ylab("Density")

ggplot(Finaldata, aes(x = percent_republican2016)) + 
    geom_density()+ ggtitle("Trump Support During the 2016 Elections") + xlab("Percent of Trump Support") + ylab("Density")

ggplot(Finaldata, aes(x = percent_republican2016)) + 
    geom_density()+ ggtitle("Trump Support During the 2016 Elections") + xlab("Percent of Trump Support") + ylab("Density") + facet_wrap(~StateColor)

>>>>

@@

#Income by state affiliation 
ggplot(Finaldata, aes(x = per_capita_income, fill = StateColor)) + 
    geom_density(alpha = .8)+ ggtitle("Income per Capita") + xlab("$") + ylab("Density")

#Trump Support 
ggplot(Finaldata, aes(x = percent_republican2016)) + 
    geom_density()+ ggtitle("Trump Support During the 2016 Elections") + xlab("Percent of Trump Support") + ylab("Density")
